---
title: "Assingment 01"
author: "Wagner Michael"
date: "23 Oktober 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1. Assign the value of 2 to a variable called a and the value of 5 to a variable called b.

```{r}
a = 2
b = 5
```

## 2. Compute the sum, difference, product and ratio of a and b (a always in the first place) and store the results to four different variables called r1, r2, r3, and r4.

```{r}
r1 = a+b
r2 = a-b
r3 = a*b
r4 = a/b
```

## 3. Create a vector v1 which contains the values stored within the four variables from step 2.

```{r}
v1 = c(r1,r2,r3,r4)
```

## 4. Add a fifth entry to vector v1 which represents a by the power of b (i.e. a**b).

```{r}
r5 = a**b
v1 = c(r1,r2,r3,r4,r5)
```

## 5. Show the content of vector v1 (e.g. use the print function or just type the variable name in a separate row).

```{r}
print(v1)
```

## 6. Create a second vector v2 which contains information on the type of mathematical operation used to derive the five results. Hence this vector should have five entries of values sum, difference,.

```{r}
v2 = c("sum", "difference", "product", "ratio", "potency")
```

## 7. Show the content of vector v2.

```{r}
print(v2)
```

## 8. Combine the two vectors v1 and v2 into a data frame called df. Each vector should become one column of the data frame so you will end up with a data frame having 5 rows and 2 columns.

```{r}
df = data.frame(v1, v2, stringsAsFactors = FALSE)

print(df)
```

## 9. Make sure that the column with the data of v1 is named "Results"" and v2 is named "Operation".

```{r}

colnames(df)[colnames(df) == 'v1'] <- 'Results'
colnames(df)[colnames(df) == 'v2'] <- 'Operation' 

```

## 10. Show the entire content of df.

```{r}
df = data.frame(v1, v2, stringsAsFactors = FALSE)
colnames(df)[colnames(df) == 'v1'] <- 'Results'
colnames(df)[colnames(df) == 'v2'] <- 'Operation'

print(df)
```

##11. Show just the entry of the 3 row and 1 column.

```{r}
df = data.frame(v1, v2, stringsAsFactors = FALSE)

df[3,1]

```



